CLT Results

### 2022-04-27 analysis/clt_irt_analysis.Rmd
add model params

```{r}
irt3_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex  |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
# eta_sex <- as_draws_df(irt3_dif_sex)%>%
#   select(b_eta_Intercept, starts_with("r_targetWord__eta"))%>%
#   mutate(iter = 1:n()) %>% 
#   pivot_longer(starts_with("r_targetWord")) %>%
#   mutate(name = str_remove(name, pattern = "r_targetWord__eta"),
#          name = str_remove_all(name, pattern = "\\[|\\]"))%>%
#   separate(name, into = c("item", "sex"), sep = "\\,")%>%
#   mutate(sex = str_remove(sex, pattern = "sex"),
#          val = b_eta_Intercept + value)%>%
#   group_by(item, sex)%>%
#   summarise(mode = estimate_mode(val),
#             uci = hdi_upper(val),
#             lci = hdi_lower(val))%>%
#   mutate(nlpar = "Easiness")
# 
# 
# alpha_sex <- as_draws_df(irt3_dif_sex)%>%
#   select(b_logalpha_Intercept, starts_with("r_targetWord__logalpha"))%>%
#   mutate(iter = 1:n()) %>% 
#   pivot_longer(starts_with("r_targetWord")) %>%
#   mutate(name = str_remove(name, pattern = "r_targetWord__logalpha"),
#          name = str_remove_all(name, pattern = "\\[|\\]"))%>%
#   separate(name, into = c("item", "sex"), sep = "\\,")%>%
#   mutate(sex = str_remove(sex, pattern = "sex"),
#          val = exp(b_logalpha_Intercept + value))%>%
#   group_by(item, sex)%>%
#   summarise(mode = estimate_mode(val),
#             uci = hdi_upper(val),
#             lci = hdi_lower(val))%>%
#   mutate(nlpar = "Discrimination")
# 
# params_sex <- bind_rows(eta_sex, alpha_sex) %>%
#   left_join(aoa%>%rename(item = targetWord))
# 
# saveRDS(params_sex, "../saves/model_params_irt3_dif_sex.rds")

@@

```{r}
irt3_dif_order <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ order  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ order  |i| targetWord),
    nl = TRUE
  ),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

>>>>

```{r}
irt3_dif_sex <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ sex  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ sex  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)

@@

```{r}
eta_sex <- as_draws_df(irt3_dif_sex)%>%
  select(b_eta_Intercept, starts_with("r_targetWord__eta"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord__eta"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val = b_eta_Intercept + value)%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  mutate(nlpar = "Easiness")

alpha_sex <- as_draws_df(irt3_dif_sex)%>%
  select(b_logalpha_Intercept, starts_with("r_targetWord__logalpha"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord__logalpha"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  separate(name, into = c("item", "sex"), sep = "\\,")%>%
  mutate(sex = str_remove(sex, pattern = "sex"),
         val = exp(b_logalpha_Intercept + value))%>%
  group_by(item, sex)%>%
  summarise(mode = estimate_mode(val),
            uci = hdi_upper(val),
            lci = hdi_lower(val))%>%
  mutate(nlpar = "Discrimination")

params_sex <- bind_rows(eta_sex, alpha_sex) %>%
  left_join(aoa%>%rename(item = targetWord))

saveRDS(params_sex, "../saves/model_params_irt3_dif_sex.rds")

@@

```{r}
irt3_dif_order <- brm(
  data = irt_dat,
  family = brmsfamily("bernoulli", "identity"),
  bf(
    correct ~ 0.25 + 0.75 * inv_logit(exp(logalpha) * eta),
    eta ~ 1 + (0+ order  |i| targetWord) + (1 | subjID),
    logalpha ~ 1 + (0+ order  |i| targetWord),
    nl = TRUE
  ),
  control = list(adapt_delta = 0.9, max_treedepth = 12),
  prior = prior_va_3pl,
  cores = 6,
  chains = 6,
  iter = 6000
)
